{\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of finite-dimensional and affine Lie algebras

### 2011-05-11 doc/paper.tex
Freudenthal formula is written

We can use Weyl character formula to obtain recurrent relation on weight multiplicities which can be used for calculations \cite{il2010folded,kulish4sfa}:

@@

Irreducible highest weight modules, BGG resolution, anomalous element.

>>>>

We can use Weyl character formula to obtain recurrent relation on weight multiplicities which can be used for calculations \cite{il2010folded,kulish4sfa}:
\begin{equation}
\label{eq:14}
m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
-\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.  
\end{equation}

@@

Another recurrent formula can be obtained from the study of Casimir elements action on irreducible highest weight modules \cite{humphreys1997introduction}:
\begin{equation}
  \label{eq:15}
  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\gek 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
\end{equation}
It is called Freudenthal multiplicity formula. It is valid for irreducible highest weight modules.
